% ============================================================
% Acknowledgement
% ============================================================

\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

\vspace{1cm}

I would like to express my sincere gratitude to all those who have contributed to the successful completion of this project.

\vspace{0.5cm}

First and foremost, I extend my heartfelt appreciation to my project supervisor, \textbf{\supervisorname}, for the continuous guidance, valuable suggestions, and encouragement throughout the development of this project. Their expertise and insights have been instrumental in shaping this work.

\vspace{0.5cm}

I am grateful to the faculty members of the \departmentname\ at \collegename\ for providing the academic foundation necessary for undertaking this project. Their teachings have equipped me with the knowledge and skills required for software development.

\vspace{0.5cm}

I would also like to thank my friends and colleagues who provided feedback, suggestions, and moral support during the development process. Their input helped improve various aspects of the application.

\vspace{0.5cm}

Special thanks go to the open-source community, particularly the developers of React, FastAPI, and the Google Gemini AI team, whose tools and technologies made this project possible.

\vspace{0.5cm}

Finally, I express my deepest gratitude to my family for their unwavering support, patience, and encouragement throughout my academic journey.

\vspace{2cm}

\noindent
\studentname

\noindent
\submissiondate
