\chapter{CONCLUSION AND FUTURE ENHANCEMENTS}

\section{Conclusion}
The \textbf{Personal Finance Manager (PFM)} project successfully demonstrates the potential of integrating Generative AI into everyday utility applications. By simplifying the expense logging process through Natural Language Processing, the system addresses the primary pain point of traditional finance apps---manual data entry friction. The use of a modern tech stack (React, FastAPI, Supabase) ensures the application is scalable, responsive, and maintainable.

The project met functionality objectives, including:
\begin{itemize}
    \item Accurate parsing of expense text using Google Gemini.
    \item Real-time data visualization for financial insights.
    \item Secure user authentication and data storage.
\end{itemize}

This system provides a robust foundation for personal financial management and showcase the practical application of Large Language Models (LLMs) in software engineering.

\section{Future Enhancements}
While the current system is functional, several enhancements can be made in future iterations:

\begin{enumerate}
    \item \textbf{Bank SMS Integration:} Automate expense logging by reading transaction SMS messages (Android only).
    \item \textbf{OCR for Receipts:} Implement Optical Character Recognition (OCR) to allow users to scan physical receipts.
    \item \textbf{Budget Alerts:} Add push notifications when users exceed their set category budgets.
    \item \textbf{Investment Tracking:} Extend the system to track investments (Stocks, Mutual Funds) alongside daily expenses.
    \item \textbf{Offline Mode:} Enhance the PWA capabilities to allow offline logging, syncing when the internet is restored.
\end{enumerate}

% -------------------------------------------------------------------
% References
% -------------------------------------------------------------------
\begin{thebibliography}{9}

\bibitem{fastapi}
FastAPI Documentation. (n.d.). \textit{FastAPI Framework}. Retrieved from \url{https://fastapi.tiangolo.com/}

\bibitem{react}
React Documentation. (n.d.). \textit{React - A JavaScript library for building user interfaces}. Retrieved from \url{https://reactjs.org/}

\bibitem{gemini}
Google Cloud. (2024). \textit{Gemini API Overview}. Retrieved from \url{https://ai.google.dev/}

\bibitem{supabase}
Supabase. (n.d.). \textit{The Open Source Firebase Alternative}. Retrieved from \url{https://supabase.com/}

\bibitem{sommerville}
Sommerville, I. (2011). \textit{Software Engineering} (9th ed.). Addison-Wesley.

\bibitem{pressman}
Pressman, R. S. (2014). \textit{Software Engineering: A Practitioner's Approach} (8th ed.). McGraw-Hill Education.

\end{thebibliography}
