\documentclass[12pt, a4paper]{report}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fancyhdr}
\usepackage{mathptmx} % Times New Roman font

% Page Layout (Top=1, Bottom=1, Right=1, Left=1.25)
\geometry{
    left=1.25in,
    right=1in,
    top=1in,
    bottom=1in
}

% Line Spacing (1.5)
\onehalfspacing

% Paragraph Style (Justified)
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

% Hyperlink Setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
    citecolor=black,
    pdftitle={Personal Finance Manager Report},
    pdfpagemode=FullScreen,
}

% Code Listing Style
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

% Heading Formatting
% Chapter Title: 16pt, Bold, Centered
\titleformat{\chapter}[display]
{\normalfont\fontsize{16}{19.2}\selectfont\bfseries\centering}{\chaptertitlename\ \thechapter}{20pt}{\fontsize{16}{19.2}\selectfont}

% Section Heading: 14pt, Bold
\titleformat{\section}
{\normalfont\fontsize{14}{16.8}\selectfont\bfseries}{\thesection}{1em}{}

% Subsection Heading: 12pt, Bold
\titleformat{\subsection}
{\normalfont\fontsize{12}{14.4}\selectfont\bfseries}{\thesubsection}{1em}{}

% Caption Formatting: Bold, 12pt
\captionsetup{font={bf, small}, labelfont=bf}

\begin{document}

% -------------------------------------------------------------------
% Title Page
% -------------------------------------------------------------------
\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
        
        \textbf{\large PERSONAL FINANCE MANAGER (PFM)}
        
        \vspace{1.5cm}
        
        \textbf{A PROJECT REPORT}
        
        \vspace{1.5cm}
        
        \textbf{SUBMITTED BY}
        
        \textbf{[Student Name]} \\
        \textbf{TU Registration No.: [Reg. No.]} \\
        \textbf{Campus Roll No.: [Roll No.]}
        
        \vspace{1.5cm}
        
        \textbf{SUBMITTED TO}
        
        \textbf{Department of Computer Science and Information Technology} \\
        \textbf{[Campus/College Name]} \\
        \textbf{Tribhuvan University}
        
        \vspace{1.5cm}
        
        In partial fulfillment of the requirements for the degree of \\
        \textbf{Bachelor of Science in Computer Science and Information Technology (B.Sc. CSIT)}
        
        \vspace{1.5cm}
        
        \textbf{[Month, Year]}
        
    \end{center}
\end{titlepage}

% -------------------------------------------------------------------
% Preliminary Pages
% -------------------------------------------------------------------
\pagenumbering{roman} % Roman numerals for prelim pages
\setcounter{page}{2} % Start counting from certificate (Title page is technically i)

% Supervisor's Recommendation
\newpage
\begin{center}
    \textbf{\large TRIBHUVAN UNIVERSITY} \\
    \textbf{\large INSTITUTE OF SCIENCE AND TECHNOLOGY} \\
    \textbf{\large [CAMPUS/COLLEGE NAME]} \\
    \textbf{\large DEPARTMENT OF COMPUTER SCIENCE AND INFORMATION TECHNOLOGY}
    
    \vspace{1cm}
    
    \textbf{\large SUPERVISOR'S RECOMMENDATION}
\end{center}
\vspace{0.5cm}
I hereby recommend that this project report prepared by \textbf{[Student Name]} entitled ``\textbf{Personal Finance Manager (PFM)}'' be accepted as a partial fulfillment of the requirements for the degree of B.Sc. in Computer Science and Information Technology. In my best knowledge, this is an original work in computer science.

\vspace{2cm}

\noindent ................................................ \\
\textbf{[Supervisor Name]} \\
Supervisor \\
Department of Computer Science and Information Technology \\
[Campus Name] \\
[Date]

% Letter of Approval
\newpage
\begin{center}
    \textbf{\large TRIBHUVAN UNIVERSITY} \\
    \textbf{\large INSTITUTE OF SCIENCE AND TECHNOLOGY} \\
    \textbf{\large [CAMPUS/COLLEGE NAME]} \\
    \textbf{\large DEPARTMENT OF COMPUTER SCIENCE AND INFORMATION TECHNOLOGY}
    
    \vspace{1cm}
    
    \textbf{\large LETTER OF APPROVAL}
\end{center}
\vspace{0.5cm}
We certify that we have examined this project report entitled ``\textbf{Personal Finance Manager (PFM)}'' submitted by \textbf{[Student Name]} and reviewed the candidate's project work. We recommend that the project report be accepted as a partial fulfillment of the requirements for the degree of B.Sc. in Computer Science and Information Technology.

\vspace{1.5cm}

\noindent \textbf{Evaluation Committee}

\vspace{1cm}

\noindent 
\begin{tabular}{lr}
................................................ & ................................................ \\
\textbf{[Supervisor Name]} & \textbf{[Head of Department Name]} \\
Supervisor & Head of Department \\
\end{tabular}

\vspace{1.5cm}

\noindent ................................................ \\
\textbf{[External Examiner Name]} \\
External Examiner

\vspace{0.5cm}

\noindent Date: ................................................


% Acknowledgement
\newpage
\chapter*{ACKNOWLEDGEMENT}
\addcontentsline{toc}{chapter}{Acknowledgement}

I would like to express my sincere gratitude to my supervisor, \textbf{[Supervisor Name]}, for their invaluable guidance, encouragement, and support throughout the course of this project. Their insights and feedback were instrumental in shaping the direction of this work.

I am also grateful to \textbf{[Head of Department Name]}, Head of the Department of Computer Science and Information Technology, for providing the necessary facilities and resources.

I would like to thank my friends and family for their unwavering support and motivation during the development of this project.

\vspace{1cm}

\noindent \textbf{[Student Name]} \\
[Date]


% Abstract
\newpage
\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{Abstract}

Managing personal finances is a crucial aspect of modern life, yet many individuals struggle with tracking expenses due to the tedious nature of manual entry and categorization. The \textbf{Personal Finance Manager (PFM)} is a hybrid mobile and web application designed to simplify expense tracking through the power of Natural Language Processing (NLP) and Artificial Intelligence.

The system allows users to log expenses using natural language phrases (e.g., ``spent 500 on lunch''), which are then parsed and categorized automatically by Google's Gemini AI. Built using a robust tech stack comprising \textbf{React.js} for the frontend, \textbf{FastAPI (Python)} for the backend, \textbf{Supabase (PostgreSQL)} for the database, and \textbf{Capacitor} for mobile deployment, the application offers a seamless cross-platform experience. Key features include intelligent expense categorization, multi-group management for shared expenses, real-time financial analytics, and a voice-enabled interface. This project demonstrates the effective integration of modern web technologies and Generative AI to solve real-world financial management problems.

\vspace{0.5cm}
\noindent \textbf{Keywords:} \textit{Personal Finance, Expense Tracking, Natural Language Processing, Artificial Intelligence, React, FastAPI, Gemini API.}

% Table of Contents
\newpage
\tableofcontents

% List of Figures
\newpage
\listoffigures

% List of Tables
\newpage
\listoftables

% List of Abbreviations
\newpage
\chapter*{LIST OF ABBREVIATIONS}
\addcontentsline{toc}{chapter}{List of Abbreviations}
\begin{tabbing}
    \hspace{3cm} \= \kill
    PFM \> Personal Finance Manager \\
    NLP \> Natural Language Processing \\
    AI \> Artificial Intelligence \\
    API \> Application Programming Interface \\
    SDLC \> Software Development Life Cycle \\
    UML \> Unified Modeling Language \\
    DFD \> Data Flow Diagram \\
    ER \> Entity Relationship \\
    UI/UX \> User Interface / User Experience
\end{tabbing}

% -------------------------------------------------------------------
% Main Content
% -------------------------------------------------------------------
\newpage
\pagenumbering{arabic} % Arabic numerals for main chapters
% Reset to 1 for introduction
\setcounter{page}{1}

\input{chapters/01_Introduction}
\input{chapters/02_Literature_Review}
\input{chapters/03_System_Analysis_and_Design}
\input{chapters/04_Implementation_and_Testing}
\input{chapters/05_Conclusion}

\end{document}
